External priors for the next generation of CMB experiments.

### 2016-02-16 Notes/CMBS4_priors_paper.tex

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_hubble_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter, H$_{0}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-h}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_omch2_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-omch2}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_scalar_amp(1)_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $A_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-as}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_hubble_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter $H_{0}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-h}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_omch2_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-omch2}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_re_optical_depth_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the optical depth $\tau$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-tau}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_massless_neutrinos_ombh2_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on the $\Omega _{b} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_neff-ombh2}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_massless_neutrinos_omch2_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_neff-omch2}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_massless_neutrinos_scalar_spectral_index(1)_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on $n_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_neff-ns}
\end{center}
\end{figure}

>>>>

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter, H$_{0}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-h}
\end{center}
\end{figure}
%==========

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_notau_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-omch2}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_tau_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $A_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-50-as}
\end{center}
\end{figure}
%==========
%
%%==========
%\begin{figure}[htbp]
%\begin{center}
%\includegraphics{{prior_omnuh2_hubble_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
%\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the Hubble parameter $H_{0}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
%\label{fig:prior_omeganuh2-50-h}
%\end{center}
%\end{figure}
%%==========
%
%
%%==========
%\begin{figure}[htbp]
%\begin{center}
%\includegraphics{{prior_omnuh2_omch2_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
%\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
%\label{fig:prior_omeganuh2-50-omch2}
%\end{center}
%\end{figure}
%%==========
%
%%==========
%\begin{figure}[htbp]
%\begin{center}
%\includegraphics{{prior_omnuh2_re_optical_depth_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
%\caption{Constraints on the sum of the neutrino masses (absolute on the left and and relative to its value on the right) as a function of priors on the optical depth $\tau$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
%\label{fig:prior_omeganuh2-50-tau}
%\end{center}
%\end{figure}
%%==========
%

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_massless_neutrinos_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on the $\Omega _{b} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_neff-ombh2}
\end{center}
\end{figure}

%\begin{figure}[htbp]
%\begin{center}
%\includegraphics{{prior_massless_neutrinos_omch2_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
%\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega_{c} h^{2}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
%\label{fig:prior_neff-omch2}
%\end{center}
%\end{figure}
%
%\begin{figure}[htbp]
%\begin{center}
%\includegraphics{{prior_massless_neutrinos_scalar_spectral_index(1)_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
%\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on $n_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
%\label{fig:prior_neff-ns}
%\end{center}
%\end{figure}
